02_LH-SIP_Quantification

### 2022-12-17 02_LH-SIP_Quantification.Rmd
changed area columns to numeric

```{r}
turnover_summarized <- turnover %>% 
  group_by(
    terrain, 
    inc_time_d,
    compound
  ) %>% 
  dplyr::summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  ) %>% 
  # Calculate generation time based off of mean of replicates
  mutate(
    # calculate generation time, converting negatives to zero
    gen_d = turnover_to_gen(u_d),

>>>>

```{r}
turnover_summarized <- turnover %>% 
  mutate(
    area2 = as.numeric(area2),
    area3 = as.numeric(area3)
  ) %>% 
  group_by(
    terrain, 
    inc_time_d,
    compound
  ) %>% 
  dplyr::summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  ) %>% 
  # Calculate generation time based off of mean of replicates
  mutate(
    # calculate generation time, converting negatives to zero
    gen_d = turnover_to_gen(u_d),
